---
title: "rvg package"
output:
  github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

[![Travis-CI Build Status](https://travis-ci.org/davidgohel/rvg.svg?branch=master)](https://travis-ci.org/davidgohel/rvg)
[![Build status](https://ci.appveyor.com/api/projects/status/github/davidgohel/rvg?branch=master)](https://ci.appveyor.com/project/davidgohel/rvg/branch/master)
[![Coverage Status](https://img.shields.io/codecov/c/github/davidgohel/rvg/master.svg)](https://codecov.io/github/davidgohel/rvg?branch=master)
[![version](http://www.r-pkg.org/badges/version/rvg)](http://www.r-pkg.org/pkg/rvg)
![cranlogs](http://cranlogs.r-pkg.org./badges/rvg)

`rvg` is a set of graphics devices that produces Vector Graphics outputs. This package 
is providing:

* SVG (*Scalable Vector Graphics*) with `dsvg`. The graphic can be made interactive 
 (tooltip, onclick and id attribute manipulation). To make that work in an HTML 
 document, check for dependencies `d3.js` in the document.
* DrawingML for Microsoft Word (>=2007) with `dml_docx`, for Microsoft PowerPoint 
  with `dml_docx` and for Microsoft Excel with `dml_xlsx`. Theses formats let users 
  edit the graphic elements (*editable graphics*) within Word, PowerPoint or Excel 
  and have a very good rendering. 

These raw XML outputs cannot be used *as is*. Function `body_add_vg` can be used with package `officer` to add vector graphics in Word documents. Function `ph_with_vg` can be used with package `officer` to add vector graphics in PowerPoint documents. By default, theses graphics are *editable*, element edition can be disabled with  option `editable = FALSE`.

```{r eval=FALSE}
library(rvg)
library(ggplot2)
library(officer)

doc <- read_pptx()
doc <- add_slide(doc, layout = "Title and Content", master = "Office Theme")
doc <- ph_with_vg(doc, code = barplot(1:10), type = "body")
print(doc, target = "my_plot.pptx")
```

## Installation

Install the development version:

```{r eval=FALSE}
devtools::install_github("davidgohel/rvg")
```

Install the CRAN version:

```{r eval=FALSE}
install.packages("rvg")
```


