---
title: "rvg package"
output:
  github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/davidgohel/rvg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/davidgohel/rvg/actions/workflows/R-CMD-check.yaml)
[![version](https://www.r-pkg.org/badges/version/rvg)](https://CRAN.R-project.org/package=rvg)
![cranlogs](https://cranlogs.r-pkg.org/badges/rvg)
<!-- badges: end -->

`rvg` provides two graphics devices that produce Vector Graphics outputs in
DrawingML format for Microsoft PowerPoint with `dml_pptx()` and for Microsoft
Excel with `dml_xlsx()`. These formats let users edit the graphic elements
(*editable graphics*) within PowerPoint or Excel and have a very good rendering.

These raw XML outputs cannot be used *as is*. The `dml()` function is a simple
wrapper that marks plot instructions as Vector Graphics instructions, so they
can be added to an Office document via `officer`:

- in PowerPoint with `officer::ph_with()`
- in Excel with `officer::sheet_add_drawing()`

```{r eval=FALSE}
library(rvg)
library(ggplot2)
library(officer)

my_vec_graph <- dml(code = barplot(1:5, col = 2:6))

doc <- read_pptx()
doc <- add_slide(doc, layout = "Title and Content", master = "Office Theme")
doc <- ph_with(doc, my_vec_graph, location = ph_location_fullsize())
print(doc, target = "my_plot.pptx")
```

For Excel workbooks, pass a `dml()` object to `officer::sheet_add_drawing()`:

```{r eval=FALSE}
doc <- read_xlsx()
doc <- sheet_add_drawing(doc, sheet = "Feuil1",
  value = dml(code = barplot(1:5, col = 2:6)),
  left = 1, top = 2, width = 6, height = 6)
print(doc, target = "vg.xlsx")
```

By default, these graphics are *editable*; element edition can be disabled with
option `editable = FALSE`.

Note that `xl_add_vg()` will be deprecated in favor of `officer::sheet_add_drawing()`.

## Installation

You can get the development version from GitHub:

```{r eval=FALSE}
devtools::install_github("davidgohel/rvg")
```

Install the CRAN version:

```{r eval=FALSE}
install.packages("rvg")
```


