---
title: "rvg package"
output:
  github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

<!-- badges: start -->
[![R-CMD-check](https://github.com/davidgohel/rvg/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/davidgohel/rvg/actions/workflows/R-CMD-check.yaml)
[![version](https://www.r-pkg.org/badges/version/rvg)](https://CRAN.R-project.org/package=rvg)
![cranlogs](https://cranlogs.r-pkg.org/badges/rvg)
<!-- badges: end -->

`rvg` is providing two graphics devices that produces Vector Graphics outputs in 
DrawingML format for Microsoft PowerPoint with `dml_pptx` and for Microsoft Excel 
with `dml_xlsx`. Theses formats let users edit the graphic elements (*editable 
graphics*) within PowerPoint or Excel and have a very good rendering. 

These raw XML outputs cannot be used *as is*. Functions `dml` and `ph_with()` 
have to be used with package `officer` to add vector graphics 
in PowerPoint documents (`dml` function is a simple wrapper to mark 
the plot instructions as Vector Graphics instructions). 

```{r eval=FALSE}
library(rvg)
library(ggplot2)
library(officer)

my_vec_graph <- dml(code = barplot(1:5, col = 2:6))

doc <- read_pptx()
doc <- add_slide(doc, layout = "Title and Content", master = "Office Theme")
doc <- ph_with(doc, my_vec_graph, location = ph_location_fullsize() )
print(doc, target = "my_plot.pptx")
```

Function `xl_add_vg()` is the equivalent for Excel workbooks. 

```{r eval=FALSE}
doc <- read_xlsx()
doc <- xl_add_vg(doc, sheet = "Feuil1", code = print(gg), 
  width = 6, height = 6, left = 1, top = 2 )
print(doc, target = "vg.xlsx")
```

By default, theses graphics are *editable*, element edition can be disabled 
with  option `editable = FALSE`. For more details, read officer article 
[graphics](https://davidgohel.github.io/officer/articles/offcran/graphics.html).

## Installation

You can get the development version from GitHub:

```{r eval=FALSE}
devtools::install_github("davidgohel/rvg")
```

Install the CRAN version:

```{r eval=FALSE}
install.packages("rvg")
```


