---
title: "rvg package"
output:
  github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

<p><a href="https://travis-ci.org/davidgohel/rvg"><img src="https://travis-ci.org/davidgohel/rvg.svg?branch=master" alt="Travis-CI Build Status" data-canonical-src="https://travis-ci.org/davidgohel/rvg.svg?branch=master" style="max-width:100%;"></a> <a href="http://cran.rstudio.com/web/packages/rvg/index.html"><img src="https://www.r-pkg.org/badges/version/rvg" alt="CRAN version" data-canonical-src="https://www.r-pkg.org/badges/version/rvg" style="max-width:100%;"></a> <img src="https://cranlogs.r-pkg.org/badges/rvg" alt="cranlogs" data-canonical-src="https://cranlogs.r-pkg.org./badges/rvg" style="max-width:100%;"></p>

`rvg` is a set of graphics devices that produces Vector Graphics outputs. This package 
is providing:

* SVG (*Scalable Vector Graphics*) with `dsvg`. The graphic can be made interactive 
 (tooltip, onclick and id attribute manipulation). To make that work in an HTML 
 document, check for dependencies `d3.js` in the document. This is the svg device used by package 
 [ggiraph](https://davidgohel.github.io/ggiraph).
* DrawingML for Microsoft PowerPoint with `dml_pptx` and for Microsoft Excel with `dml_xlsx`. Theses formats let users edit the graphic elements (*editable graphics*) within PowerPoint or Excel and have a very good rendering. 

These raw XML outputs cannot be used *as is*. Functions `ph_with_vg` and `ph_with_vg_at` can be used with package `officer` to add vector graphics in PowerPoint documents. By default, theses graphics are *editable*, element edition can be disabled with  option `editable = FALSE`.

```{r eval=FALSE}
library(rvg)
library(ggplot2)
library(officer)

doc <- read_pptx()
doc <- add_slide(doc, layout = "Title and Content", master = "Office Theme")
doc <- ph_with_vg(doc, code = barplot(1:10), type = "body")
print(doc, target = "my_plot.pptx")
```

## Installation

Install the development version:

```{r eval=FALSE}
devtools::install_github("davidgohel/rvg")
```

Install the CRAN version:

```{r eval=FALSE}
install.packages("rvg")
```


