---
title: "Customizing rvg objects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Customizing rvg objects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include=FALSE}
library(knitr)
library(openssl)
library(htmltools)
opts_chunk$set(echo = TRUE)

image_html <- function(x, class = NULL){
  input <- normalizePath(x, mustWork = TRUE)
  base64 <- lapply(input, function(z){
    buf <- readBin(z, raw(), file.info(z)$size)
    base64_encode(buf, linebreaks = FALSE)
  })
  img <- lapply(base64, function(z){
    div( class = "img_slide", tags$img(src = paste0("data:image/png;base64,", z)) )
  })
  if( !is.null(class) )
    div(class=class, tagList(img))
  else div(tagList(img))
}
pptx_to_image <- function( url, class = NULL ){
  file <- url
  cmd_ <- sprintf(
    "/Applications/LibreOffice.app/Contents/MacOS/soffice --headless --convert-to pdf --outdir %s %s",
    dirname(file), file )
  system(cmd_)
  
  pdf_file <- gsub("\\.(docx|pptx)$", ".pdf", file)
  screen_copies <- pdftools::pdf_convert(pdf = pdf_file, format = "png", verbose = FALSE)
  on.exit(unlink(c(pdf_file, file, screen_copies)))
  image_html(screen_copies, class = class)
}
```

```{css echo=FALSE, eval=TRUE}
.img_slide img {
  border: gray 1px solid;
  width: 100%;
}
.row.vertical-align {
  display: flex;
  align-items: center;
}
```

## Fonts 

When you use specific fonts, you will need that font installed on your system.
This can be check with package `gdtools` and function `gdtools::font_family_exists()`.

```{r}
gdtools::font_family_exists("Roboto")
```

To use that font with package `rvg`, best is to use the argument `fonts` (see `dml_pptx()`).
It's a named list that can contains 4 font family names, one per family type: `sans`, 
`serif`, `mono` and `symbol`. 

The following example illustrates how to use font *Roboto* as *sans* family.

```{r eval=gdtools::font_family_exists("Roboto")}
library(ggplot2)
library(officer)
library(rvg)

z <- ggplot(data = iris, 
  mapping = aes(x = Sepal.Length, y = Petal.Width)) +
  geom_point() + labs(title = "With font Bradley Hand") +
  theme_minimal(base_family = "sans", base_size = 18)

graph_editable <- dml(ggobj = z, fonts = list(sans = "Bradley Hand"))
```


<div class="row vertical-align">

<div class="col-12 col-sm-6 col-md-6">

```{r}
doc <- read_pptx()
doc <- add_slide(doc)
doc <- ph_with(x = doc, graph_editable,
   location = ph_location_type(type = "body") )
print(doc, target = "rvg.pptx")
```

</div>

<div class="col-12 col-sm-6 col-md-6">

```{r echo=FALSE}
pptx_to_image("rvg.pptx")
```

</div>

</div>

## Background color

Background color can be controled with argument `bg`: 

<div class="row vertical-align">

<div class="col-12 col-sm-6 col-md-6">

```{r}
anyplot = dml(code = barplot(1:5, col = 2:6), bg = "wheat")

doc <- read_pptx()
doc <- add_slide(doc)
doc <- ph_with(doc, anyplot, location = ph_location_fullsize())

print(doc, target = "bg.pptx")
```

</div>

<div class="col-12 col-sm-6 col-md-6">

```{r echo=FALSE}
pptx_to_image("bg.pptx")
```

</div>

</div>




When dealing with a ggplot object argument `bg` will have no effect as 
themes are specifying background color: 

<div class="row vertical-align">

<div class="col-12 col-sm-6 col-md-6">

```{r}
z <- z + theme(
  panel.background = element_rect(fill = "#EFEFEF"), 
  plot.background = element_rect(fill = "wheat"))
graph_editable <- dml(ggobj = z, fonts = list(sans = "Bradley Hand"))

doc <- read_pptx()
doc <- add_slide(doc)
doc <- ph_with(doc, graph_editable, location = ph_location_fullsize())

print(doc, target = "ggbg.pptx")
```

</div>

<div class="col-12 col-sm-6 col-md-6">

```{r echo=FALSE}
pptx_to_image("ggbg.pptx")
```

</div>

</div>
